Robustly decorrelating errors with mixed quantum gates

### 2019-08-25 decorrelation/mixed_unitaries.tex
Moved 2Q figure file

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. These error Hamiltonians lie in a vector space, which we illustrate as two-dimensional here. a) Four effective Hamiltonians. The origin is not contained in their convex hull, so there are no MQGs. b) After including an additional control solution, the convex hull grows to contain the origin, and so an MQG exists. c) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a MQG may drift, leading to a first-order error. d) The derivatives also lie in a vector space. If the origin lies in their convex hull, then it may be possible to construct a MQG. \kcy{Split this figure into two.}}
  \label{fig:vectorspace}
\end{figure}

@@

\kcy{move this later}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace2.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. a) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a MQG may drift, leading to a first-order error. b) The derivatives also lie in a vector space. If the origin lies in their convex hull $\mathsf{Conv}(\{H_k \otimes H_{k,1} \oplus H_{k,2} \oplus \cdots\}_k)$ then it may be possible to construct a robust 1-MQG.}
  \label{fig:vectorspace}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
  \caption{\kcy{Axis label is screwed up} Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RY(\frac{\pi}{2})$. The results are qualitatively similar to those for $RX(\frac{\pi}{2})$. In this case the 0MQG outperforms both the 1MQG by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin. However, varying over $\delta$ we see that the 1MQG outperforms the 0MQG by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes.}
  \label{fig:YMQG}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{2q_robustness.png}
  \caption{\kcy{needs to be on previous page} Numerical results comparing a 0MQG to a 1MQG for a pair of tunable qubits, with a resonant exchange interaction. Shown with lower alpha values are example constituent controls. The 0MQG and 1MQG can be seen to outperform these controls by half of an order of magnitude at the origin. For all detuning values the 1MQG performs as well or better than the 0MQG. When there is $.2\%$ drift in the qubit frequency, the 1MQG outperforms members of the control families by almost an order of magnitude in diamond norm. Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MQG outperforms the the constituent controls by over half an order of magnitude.}
  \label{fig:2MQG}
\end{figure}

@@

Another interesting area of research would be using model-free approaches. The numerical work in the paper assumes access to a model of the system, however an experimentalist may not have a model readily available to describe the system, e.g. in the presence of unknown on-chip crosstalk, or an uncalibrated transfer function of the system. Even if a model is available, it might be computationally inconvenient to simulate, i.e. for more than a few qubits. In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nelder-Mead to perform the minimization. While performing a complete optimization in this way would require full process tomography, one could instead optimize via partial tomography. By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.
% ==============================================================================
% Section: Acknowledgements
% ==============================================================================

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. These error Hamiltonians lie in a vector space, which we illustrate as two-dimensional here. a) Four effective Hamiltonians. The origin is not contained in their convex hull, so there are no MQGs. b) After including an additional control solution, the convex hull grows to contain the origin, and so an MQG exists. c) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a MQG may drift, leading to a first-order error. d) The derivatives also lie in a vector space. If the origin lies in their convex hull, then it may be possible to construct a MQG.}
  \label{fig:vectorspace}
\end{figure}

@@

\kcy{This shoudl probably use the comma derivative notation that we use in the figures. Should the figures change from H to something else?}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{vectorspace2.pdf}
  \caption{A target unitary gate can be implemented a number of ways, each with a different effective Hamiltonian error. a) The error Hamiltonians shown with their derivative with respect to a control parameter. As this parameter drifts, a MQG may drift, leading to a first-order error. b) The derivatives also lie in a vector space. If the origin lies in their convex hull $\mathsf{Conv}(\{H_k \otimes H_{k,1} \oplus H_{k,2} \oplus \cdots\}_k)$ then it may be possible to construct a robust 1-MQG. \kcy{This should appear in the main text somewhere. When we add the derivatives we make our space larger, but we still want the origin to be in the higher-dimensional convex hull.}}
  \label{fig:vectorspace}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{SQRTY_no_member.png}
  \caption{\kcy{Axis label is screwed up. Should we replot these as in the 2Q example?} Numerical results comparing a 0MQG to a 1MQG for a single tunable qubit, for $RY(\frac{\pi}{2})$. The results are qualitatively similar to those for $RX(\frac{\pi}{2})$. In this case the 0MQG outperforms both the 1MQG by two orders of magnitude, and the constituent controls by three orders of magnitude at the origin. However, varying over $\delta$ we see that the 1MQG outperforms the 0MQG by up to an order of magnitude when there is $.1\%$ drift in the qubit control amplitudes. }
  \label{fig:YMQG}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{figures/2q_robustness.pdf}
  \caption{\kcy{needs to be on previous page} Numerical results comparing a 0MQG to a 1MQG for a pair of tunable qubits, with a resonant exchange interaction. Shown with lower alpha values are example constituent controls. The 0MQG and 1MQG can be seen to outperform these controls by half of an order of magnitude at the origin. For all detuning values the 1MQG performs as well or better than the 0MQG. When there is $.2\%$ drift in the qubit frequency, the 1MQG outperforms members of the control families by almost an order of magnitude in diamond norm. Similarly, for $.2\%$ drift in the qubit control amplitude, we see that the 1MQG outperforms the the constituent controls by over half an order of magnitude.}
  \label{fig:2MQG}
\end{figure}

@@

Another interesting area of research would be using model-free approaches. The numerical work in the paper assumes access to a model of the system, however an experimentalist may not have a model readily available to describe the system, e.g. in the presence of unknown on-chip crosstalk, or an uncalibrated transfer function of the system. Even if a model is available, it might be computationally inconvenient to simulate, i.e. for more than a few qubits. In these situations, one approach would be to use \textit{in-situ} optimal control techniques \cite{Wu2018, Kelly2014, Ferrie2015} to generate candidate controls, and then use an optimizer like Nelder-Mead to perform the minimization. While performing a complete optimization in this way would require full process tomography, one could instead optimize via partial tomography. By selecting pre-- and post --rotations that correspond to measuring Pauli-moments of interest in the Hamiltonian, such as unwanted $Z\otimes Z$ crosstalk, one could perform optimization over fewer parameters.

% ==============================================================================
% Section: Acknowledgements
% ==============================================================================
